### 2016-03-10 paper/paper.tex
some more small paper changes

This choice of weights will reproduce actions which lead to a higher reward with
higher probability but will also choose suboptimal actions with some
probability, because our new policy can not be too far away in terms of KL
divergence from the old policy and we start with a random policy. This achieves
a trade-off between exploration and exploitation.

@@

\newcommand\nkb{\#\mathit{kb}}
\newcommand\nep{\#\mathit{ep}}
\newcommand\nst{\#\mathit{st}}

To simulate the kilobots and collect samples for the object movement policy we
wrote our own simple kilobot simulator (\autoref{fig:simulator}) in Python based
on the 2D physics engine pybox2d\cite{pybox2d}. This allows us to simulate
collisions between kilobots and other kilobots, the object and walls.

@@

After that we compute the distance for the other dimensions (light positions for
$K$ and light positions and actions for $K'$) as
$$
d_{other} = (x_1 - x_2)^T \mathrm{diag}\left(\frac{1}{\sigma_{x}^2}\right) (x_1 - x_2),
$$
where $x_1$ and $x_2$ are vectors holding the values for all non-kilobot
dimensions and $\sigma_x$ is the non-kilobot bandwidth.

@@

In our experiments we used $w = 0.5$ and recomputed $\sigma_{kb}$ and $\sigma_x$
in each iteration as the square root of the median of the squared distances
between all sample values for each dimension separately. We also scaled the
bandwidths uniformly in each dimension by some manually specified factors.

@@

The policies start of only being able to push the object when the kilobots start
to the left of the object. After about 5 iterations they can also handle kilobot
starting positions above and below the object by first moving the kilobots to
the left and down and then pushing the object from the left side. After further
iterations the policies are able to push the object to the right even if the
kilobots start above and to the right of the object (see
\autoref{fig:policyEvolution}). With even more iterations the kilobot starting
positions from which the object can be pushed tend to extend even further, but
this improvement is inconsistent and the policies may even get worse again.
Therefore we manually inspected the policies at each iteration and chose a good
policy (which is typically found in the first about 15 iterations) for solving
the maze.

@@

With improving policies the object can be pushed to the right from a larger
number of kilobot starting positions and therefore the reward tends to increase
(see \autoref{fig:meanReward}).

>>>>

This choice of weights will reproduce actions which lead to a higher reward with
higher probability but will also choose suboptimal actions with some
probability. This behavior occurs because our new policy can not be too far away
in terms of KL divergence from the old policy and we start with a random policy.
This achieves a trade-off between exploration and exploitation.

@@

\newcommand\nkb{n_\mathit{kb}}
\newcommand\nep{n_\mathit{ep}}
\newcommand\nst{n_\mathit{st}}

We did not use a general purpose robot simulator like V-REP\cite{vrep}, because
it would take much longer than necessary to generate samples as the kilobots are
simulated more accurately than needed for our task. Instead we wrote our own
simple kilobot simulator (\autoref{fig:simulator}) in Python based on the 2D
physics engine pybox2d\cite{pybox2d}. This allows us to simulate collisions
between kilobots and other kilobots, the object and walls.

@@

After that we compute the distance for the other dimensions (light positions for
$K$ and light positions and actions for $K'$) as
$$
d_{other} = (x_1 - x_2)^T \mathrm{diag}\left(\frac{1}{\sigma_{other}^2}\right) (x_1 - x_2),
$$
where $x_1$ and $x_2$ are vectors holding the values for all non-kilobot
dimensions and $\sigma_{other}$ is the non-kilobot bandwidth.

@@

In our experiments we used $w = 0.5$ and recomputed $\sigma_{kb}$ and
$\sigma_{other}$ in each iteration as the square root of the median of the
squared distances between all sample values for each dimension separately. We
also scaled the bandwidths uniformly in each dimension by some manually
specified factors.

@@

The policies start of only being able to push the object when the kilobots start
to the left of the object. After about 5 iterations they can also handle kilobot
starting positions above and below the object by first moving the kilobots
around to the left side of the object and then pushing the object from the left
side. After further iterations the policies are able to push the object to the
right even if the kilobots start above and to the right of the object (see
\autoref{fig:policyEvolution}). With even more iterations the kilobot starting
positions from which the object can be pushed tend to extend even further, but
this improvement is inconsistent and the policies may even get worse again.
Therefore we manually inspected the policies at each iteration and chose a good
policy (which is typically found in the first about 15 iterations) for solving
the maze.

@@

With improving policies the object can be pushed to the right from a larger
number of kilobot starting positions. Additionally the object can be pushed
faster and with less vertical movement. Therefore the reward tends to increase
(see \autoref{fig:meanReward}).
